\section{Research Experience}
\textbf{Monterrey Institute of Technology, Photonics and Mathematical Optics Group} \hfill{\bf Sep 2023 -- present}

Advisors: Julio C. Gutierrez-Vega  \href{https://scholar.google.com/citations?user=SXtXBWkAAAAJ&hl=en}{\aiGoogleScholar}

\begin{itemize}
\setlength{\itemsep}{0.5em}
    \item Implemented a Boundary Integral Method for solving the Lippmann-Schwinger (scattering) Equation.
    \item Implementation of meshes for discretization and parallel computation.
    \item Advanced theoretical methods and mathematical formulations for analytic results.
    %\item Gave a poster presentation at the \href{https://photonics-mexico.com/mopm2023/}{Mexican Optics \& Photonics Meeting}.\dotfill{\bf Nov 2023}
\end{itemize}
\medskip
{\bf International Centre for Theoretical Physics \& Quantinuum}\hfill{\bf Apr 2023}\\
Advisor: Nathan Fitzpatrick \orcidlink{0000-0001-5819-9129} (\emph{Quantinuum})
\begin{itemize}
\setlength{\itemsep}{0.5em}
    \item Generated ground and excited state curves using a Quantum Krylov-subspace method along a reaction coordinate for an H\textsubscript{2} molecular Hamiltonian.
    \item Development of hybrid quantum-classical algorithms with TKET and the InQuanto quantum chemistry platform; aided team in setting up and using \textbf{Git} for version control.
    \item Collaborated with graduate students from diverse backgrounds. Our team received the \emph{Best Team Project} award, along with second place.
%    \item Attended lectures on Quantum Adiabatic Computation, Quantum Error Correction, Quantum Chemistry, and ZX calculus.
\end{itemize}
\medskip
%\begin{minipage}[t][][t]{\textwidth}
% \textbf{Monterrey Institute of Technology, Nano \& Microstructures RG} \hfill {\bf Jan 2023 -- Jul 2023}
% 
% Advisors: Flavio F. Contreras \orcidlink{0000-0003-2375-131X}
% 
% \begin{itemize}
%     \item Charaterization of molecular order and functional properties of wheat samples in order to determine relative crystallinity-degrees.
%     \item Analysis of the Debye Scattering Equation and atomic Pair-Distribution Function (PDF) for structural determination of ferrispinels and Fm-3m symmetries.
%     \item Experience handling AFM, XRD, UV-VIS, FTIR, Raman Spectrometers, as well as PVD techniques.
% \end{itemize}
% %\end{minipage}
% 
% \medskip
%\begin{minipage}[t][][t]{\textwidth}
\textbf{Monterrey Institute of Technology, Physics Dept.}\hfill {\bf Aug 2021 -- Sep 2022}

Advisors: Dr. Antonio Ortiz-Ambriz \orcidlink{0000-0002-8302-0861} Dr. Gerardo Fox \orcidlink{0000-0002-7696-0767} Dr. Servando López \orcidlink{0000-0002-8492-1709}

\begin{itemize}
\setlength{\itemsep}{0.5em}
    \item Numerical simulation of the \emph{Nonlinear Schrodinger Equation} through \emph{pseudo-spectral method} (split-step Fourier) and numerical solutions of Boundary Value Problems (shooting method, finite differences, etc.).
    \item Developed audio-identification algorithm in order to identify an audio recording from a microphone (FFT and signal-processing methods).
    \item Analyzed the travelling-salesman-problem through simulated annealing; simulated the dynamics and critical points of the Lenz-Ising model.
    \item Developed \textbf{Genetic algorithms} and \textbf{Neural Networks}; Experience with \textbf{Agent Based Modeling}.
\end{itemize}